---
title: "DiabetesGraph"
author: "Lampros"
date: "January 18, 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(shiny)
library(dplyr)
library(data.table)
library(ggplot2)
```

## Purpose
  
  
The purpose of this sample app is to enable persons with diabetes easily graph their Insulin dosage and Glucose levels.  
This allows the user to have a better view of the trends that his glucose follows and to adapt the Insulin dosage.

This application is used for **Demonstration purpose only** and the data may be inaccurate or false. Please do not use for medical or any other purpose.

All the code for the ShinyApp, Documentation and Presentation can be found at my Github repository  

<a href="https://github.com/lcfgr/dataproducts">Github Data Products repository</a>

## Procedure

- The user must upload a .csv type of file (See documentation for details)
- Afterward he can select the parameters of .csv file
- Press Process button
- Choose the Plot parameters
- Press Plot button

## Code for sample Graph
The following code is part of the shinyApp and is used to create a sample Plot
```{r, echo = T,message=F, comment=F }
All_data<- data.table::fread("diabetes_data.csv")
Glucose_data <- select(All_data,c(contains("Date"),contains("Glucose")))
Glucose_data<- melt(Glucose_data,id.vars = "Date", variable.name = "Time")
levels(Glucose_data$Time) <- c("08:00","13:00","20:00")
Glucose_data<-
  Glucose_data[,datetime:=as.POSIXct(
    paste(All_data$Date, as.character(Glucose_data$Time)))]
plot_data <- Glucose_data
p <- ggplot(plot_data, aes(x= plot_data$datetime, y=plot_data$value))
p <- p + geom_point()
p <- p + stat_smooth(method = "loess", formula = y ~ x, size=1)
p <- p + ggtitle("Glucose/time Graph") + labs(x="Time",y="Glucose(mg/dl)")

```

## Sample Plot

```{r pressure}
plot(p)
```

